The method presented here for an alternative to the continuation approach suggested by \cite{Mulder2017Jul} still has quite a few problems. First of all the $4^{\circ}$ resolution together with the limited number of depth layers is one of the main problems. The limited depth layers fail to accuratly capture even the present day overturning circulation. Here we note that the same can be said for a model with present day forcings as noted in \cref{sec:mocQual}. Next, we also note that an ACC strength of just $80 Sv$ is a lot lower than the observed 100-150 Sv. This can mainly be attributed to the weaker wind forcings in the southern hemisphere. The present day zonal wind forcing being more than $50 \%$ stronger.

The possibility of using a 1 or 2 degree Veros model for this paper was extensively explored. But issues often arose with the exact values of constants and frequent invalid value errors to do with eddy kinetic energy could not be fixed in time for this paper.

The 4 degree model also took quite a bit of time to be adapted for the customized forcings and bathymetries. This is due to the fact that the method for determining boundary conditions for islands would often find more islands than exist in the model. Resulting in having to customize each setup individually for its bathymetry to accept the islands present. This is also why $180^{\circ} E$ was used as the boundary longitude instead of the default $0^{\circ}$. 

Another major thing that is generally neglegted in this paper is the total absence of change in surface forcings. Even though it is known that these change drastically even in short time spans. We also have some general knowledge of global average temperature for the time period discussed here. However the search for a dataset for each time step has proven futile. Often large uncertainties exist. This left us with the decision to not bother with any changes in the forcings. Even though there have been massive changes in the time period discussed here. Coupled with the sensitive nature of GCM's we suggest taking the results in this paper with a grain of salt. 

A lot of future research is possible in the topic of oceanic throughflow. More accurate bathymetries are being produced due to breakthroughs in geological techniques (\cite{Baatsen2016Aug}). These, coupled with a higher resolution model will probably result in even more accurate depictions of the past oceanic systems. Research on this topic is of particular importance because of the present day observed changes in strength of the MOC.