\subsection{Control setup}

To have an idea of the quality of the model and thus if any of the results resemble reality, one can compare the present day setup of the model to an existing model with realistic forcings. Also, the model can be compared to another similar model. This can be a useful tool to see what aspects of the present day situation are captured by the model and more importantly which nuances are lost. General circulation models with a resolution comparable to the model used in this paper often loose major features having to do with deep water flows. Especially the restoring boundary conditions at the surface are troublesome where capturing artifacts of the thermohaline circulation is highly dependant on surface salinity and temperature profiles.


 


\subsubsection{Quality of BSF}
Too look at the quality of the barotropic stream function we compare the barotropic stream function of our model to a $4^{\circ}$ model with realistic forcings. This model was made with the standard Veros setup with custom open Indonesian passage. In \fref{fig:bsf_compared} we see that the barotropic stream function itself is remarkably similar. Only showing a weaker subtropical gyre in the Indian ocean and a weaker gulf stream. In the temperature profile at 245 meters in depth there are however larger discrepancies. There is a $4^{\circ}C$ difference in temperature in the gulf stream and a $2^{\circ}C$ temperature difference in the Kuroshio gyre. This can be attributed to weaker SST forcing at the surface on these places because of the zonal mean nature of these forcings and also due to the shorter runlength of the model. Thus the model did not yet get addequate time to fully develop the flows (THIS COULD BE BETTER)

